---
title: "R for Data Analysis"
description: |
  This site is the landing page for the workshops delivered at Juspay.
author:
  - name: Ayush Patel
    url: https://ayushpatel.netlify.app/
    affiliation: RStudio Certified tidyverse Instructor
    affiliation_url: https://education.rstudio.com/trainers/people/patel+ayush/
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    theme: bespoke-theme.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Pre-workshop setup

<iframe src="https://giphy.com/embed/2UwIatkqCtPuQs5sgV" width="480" height="402" frameBorder="0" class="giphy-embed" allowFullScreen></iframe><p><a href="https://giphy.com/gifs/cbc-schittscreek-schitts-creek-2UwIatkqCtPuQs5sgV">via GIPHY</a></p>

Hello! Here is the minimum setup you would need to get the most out of the workshop. Please check if you have these minimum requirements or higher, either are fine. In case you don't, follow the links to set it up.

  > A recent version of R (>=3.9.0), which is available for free at https://cran.r-project.org/

<br>

   > A recent version of RStudio Desktop (>=1.3.0), available for free at https://www.rstudio.com/download (RStudio Desktop Open Source License)
   
<br>

  > The R packages we will use, which you can install by connecting to the internet, opening RStudio, and running at the command line:

```{r code_installpackages, eval=FALSE, echo=TRUE}
install.packages(c("tidyverse", "rmarkdown", "shiny", "flexdashboard"))
```



